Will Kamala Harris will win the 2024 Presidential election

### 2024-11-04 paper/paper.qmd
edits to paragraph structure
.

Arizona is a very important swing state especially as the state has switches which party they voted for in in the last two elections with Trump winning 49% of the vote and Clinton with 45.5%, which considering Arizona is a swing state is a rather significant6 margin. While in the 2020 election Biden ended up winning Arizona with 49.4% of the vote and Trump 49.1%, which is a much smaller margin of victory and what makes Arizona so questionable in the 2024 election. We can see in @fig-supportAM that while the polling numbers for Harris started somewhat low around 42%, the have gone up significantly and have continued to trend upwards in the most recent polls. Although, in the @fig-supportstate trump still has larger support in the state, and the largest polling difference in Trump's favour out of all the swing states polled @towin270.

@@

Harris is currently leading the polls in Michigan with 49% of the vote and Trump with 47%, this is a rather slim margin, but the first in the discussed states where Harris is leading in the polls. In @fig-supportAM we can see that there was a significant jump for Harris and a small dip in October followed by a gradual increase leading up to the elections. When we look at the voting history of the state in the last two elections, the have voted for the same candidates as Arizona and Georgia, where they voted for Biden in 2020 and for Trump in 2016, with the voting percentages at 50.6% to 47.8% in 2020 and 47.5% to 47.3 in 2016 with respect to the winner. Although unlike the previously mentioned states 2016 was the first time the state voted for the republican candidate since 1992. Considering Michigan is home to the largest black majority city in the United states, Detroit, and a large majority of union workers who often vote democratic as it is seen as the more union-friendly party between the two it is rather like that Harris will win the state @towin270.

@@

- integrate more context, and more vairables : Future studies could examine how state-level socioeconomic and political factors, such as unemployment rates, healthcare concerns, or local election issues, might influence voter preferences in each swing state. This would add depth to the model and align predictions more closely with real-world factors.

>>>>

Arizona is a very important swing state especially as the state has switches which party they voted for in in the last two elections with Trump winning 49% of the vote and Clinton with 45.5%, which considering Arizona is a swing state is a rather significant6 margin. While in the 2020 election Biden ended up winning Arizona with 49.4% of the vote and Trump 49.1%, which is a much smaller margin of victory and what makes Arizona so questionable in the 2024 election.

We can see in @fig-supportAM that while the polling numbers for Harris started somewhat low around 42%, the have gone up significantly and have continued to trend upwards in the most recent polls. Although, in the @fig-supportstate trump still has larger support in the state, and the largest polling difference in Trump's favour out of all the swing states polled @towin270.

@@

Harris is currently leading the polls in Michigan with 49% of the vote and Trump with 47%, this is a rather slim margin, but the first in the discussed states where Harris is leading in the polls. In @fig-supportAM we can see that there was a significant jump for Harris and a small dip in October followed by a gradual increase leading up to the elections. When we look at the voting history of the state in the last two elections, the have voted for the same candidates as Arizona and Georgia, where they voted for Biden in 2020 and for Trump in 2016, with the voting percentages at 50.6% to 47.8% in 2020 and 47.5% to 47.3 in 2016 with respect to the winner.

Although unlike the previously mentioned states 2016 was the first time the state voted for the republican candidate since 1992. Considering Michigan is home to the largest black majority city in the United states, Detroit, and a large majority of union workers who often vote democratic as it is seen as the more union-friendly party between the two it is rather like that Harris will win the state @towin270.

@@
